Ice sheet mass flows

### 2024-06-29 sankey.tex
tiny correction
Formatting
Labels from table

\begin{document}
\begin{tikzpicture}[remember picture, overlay, shift={(5.5,-1.5)}]

@@

    \newcommand\abovelabel[2]{ % valname, label
      \node[font=\tiny, rotate=45, anchor=north west]
      at ([yshift=5mm,xshift=-3mm]#1.center) {\qq{#1}: #2};
    }
    \newcommand\belowlabel[2]{ % valname, label
      \node[font=\tiny, rotate=45, anchor=north east]
      at ([yshift=-2mm,xshift=0mm]#1.center) {#2: \qq{#1}};
    }

@@

    \abovelabel{SF}{Snowfall}
    \abovelabel{DP}{Deposition}
    \abovelabel{CD}{Condensation}
    \abovelabel{RF}{Rainfall}

@@

    \sankeyadvance[out-red]{FLa}{10mm}
    \sankeyend[out-red]{FLa}
    \belowlabel{FLa}{Frontal retreat}

    \ifnum \numexpr\Q{vMG} > \Q{vML}
      \sankeynode{name=MGa, quantity=\qq{MG},
        at={[xshift=3mm,yshift=-3mm]MG.left}, anchor=left, angle=0}

      \node[font=\tiny, anchor=north]
      at ([yshift=0mm,xshift=3mm]MGa.south) {\qq{MGa}: Mass gain};

      \sankeyoutin{MG}{MGa}
    \fi

@@

    \ifthenelse{\Q{vMG} < \Q{vML}} {
      %% mass loss
      \sankeynode{name=ML, quantity=\Q{vML},
        at={[xshift=-\xoff]RF.right}, anchor=left} %, angle=-45}
      \abovelabel{ML}{Drawdown}

@@

      \sankeystart[red]{ML}
      \sankeyadvance[red-to-ice]{ML}{5mm}
      \sankeyoutin{ML}{MLi}
    }{
      %% mass gain
      \sankeyadvance[ice-to-black]{MGa}{3mm}
      \sankeyend[black]{MGa}

      % frontal with no drawdown
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[yshift=15mm,xshift=3mm]RFZi.right}, anchor=left}
    }

@@

    \belowlabel{RU}{Runoff}
    \belowlabel{BMa}{Basal melting}
    \belowlabel{SUBa}{Submarine melting}
    \belowlabel{D}{Calving}
    \belowlabel{GZa}{Grounding line retreat}

    \node[font=\tiny, rotate=45, anchor=north east]
    at ([yshift=1mm,xshift=3mm]SUaa.south) {Sublimation: \qq{SUaa}};

    \node[font=\tiny, rotate=45, anchor=north east]
    at ([yshift=0mm,xshift=5mm]EVa.north) {Evaporation: \qq{EVa}};

    \node[font=\tiny, anchor=west, rotate=90]
    at ([yshift=-0.5mm,xshift=1mm]RFZo.center) {Refreezing: \qq{RFZi}};

>>>>

\begin{document}

\selectcolormodel{cmyk} % Can be rbg or cmyk, cmyk is better for printing

\begin{tikzpicture}[remember picture, overlay, shift={(5.5,-1.5)}]

@@

    \newcommand\abovelabel[1]{ % valname
      \node[font=\tiny, rotate=45, anchor=north west]
      at ([yshift=5mm,xshift=-3mm]#1.center) {\qq{#1}: \Lab{v#1}};
    }
    \newcommand\belowlabel[2]{ % valname
      \node[font=\tiny, rotate=45, anchor=north east]
      at ([yshift=-2mm,xshift=0mm]#1.center) {\Lab{#2}: \qq{#1}};
    }

@@

    \abovelabel{SF}
    \abovelabel{DP}
    \abovelabel{CD}
    \abovelabel{RF}

@@

    \sankeyadvance[out-red]{FLa}{10mm}
    \sankeyend[out-red]{FLa}
    \belowlabel{FLa}{vFRLOSS}

    \ifnum \numexpr\Q{vMG} > \Q{vML}
      \sankeynode{name=MGa, quantity=\qq{MG},
        at={[xshift=3mm,yshift=-3mm]MG.left}, anchor=left, angle=0}
      \node[font=\tiny, anchor=north]
      at ([yshift=0mm,xshift=3mm]MGa.south) {\qq{MGa}: Mass gain};
      \sankeyoutin{MG}{MGa}
    \fi

@@

    \ifthenelse{\Q{vMG} < \Q{vML}} { % mass loss
      \sankeynode{name=ML, quantity=\Q{vML}, at={[xshift=-\xoff]RF.right}, anchor=left}
      \abovelabel{ML}

@@

      \sankeystart[red]{ML}
      \sankeyadvance[red-to-ice]{ML}{5mm}
      \sankeyoutin{ML}{MLi}
    }{ % mass gain
      \sankeyadvance[ice-to-black]{MGa}{3mm}
      \sankeyend[black]{MGa}
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[yshift=15mm,xshift=3mm]RFZi.right}, anchor=left}
    }

@@

    \belowlabel{RU}{vRU}
    \belowlabel{BMa}{vBM}
    \belowlabel{SUBa}{vSUB}
    \belowlabel{D}{vICE}
    \belowlabel{GZa}{vGZRET}

    \node[font=\tiny, rotate=45, anchor=north east]
    at ([yshift=1mm,xshift=3mm]SUaa.south) {\Lab{vSU}: \qq{SUaa}};

    \node[font=\tiny, rotate=45, anchor=north east]
    at ([yshift=0mm,xshift=5mm]EVa.north) {\Lab{vEV}: \qq{EVa}};

    \node[font=\tiny, anchor=west, rotate=90]
    at ([yshift=-0.5mm,xshift=1mm]RFZo.center) {\Lab{vRFZ}: \qq{RFZi}};
